The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-07 author.tex
s/Víctor Terrón/V. Terrón — like the other authors
Also, include the city in the affiliation.
Add ORCID number

\author{S. Conseil}
\affiliation{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis-Laval, France}

@@

\author[0000-0001-5982-167X]{T. Jenness}
\affiliation{Large Synoptic Survey Telescope, 950 N Cherry Ave, Tucson, AZ, 85719}

@@

\author[0000-0001-9898-5597]{L. P. Singer}
\affiliation{Astroparticle Physics Laboratory, \afgoddard}

@@

\author{V\'{i}ctor Terr\'{o}n}
\affiliation{Institute of Astrophysics of Andalusia (IAA-CSIC), Spain}

@@

\author{B. A. Weaver}
\affiliation{National Optical Astronomy Observatory, 950 N. Cherry Ave., Tucson, AZ 85719}

>>>>

\author[0000-0002-3657-4191]{S. Conseil}
\affiliation{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis-Laval, France}

@@

\author[0000-0001-5982-167X]{T. Jenness}
\affiliation{Large Synoptic Survey Telescope, 950 N. Cherry Ave., Tucson, AZ, 85719, USA}

@@

\author[0000-0001-9898-5597]{L. P. Singer}
\affiliation{Astroparticle Physics Laboratory, \afgoddard}
\affiliation{Joint Space-Science Institute, University of Maryland, College Park, MD 20742, USA}

@@

\author{V. Terr\'{o}n}
\affiliation{Institute of Astrophysics of Andalusia (IAA-CSIC), Granada, Spain}

@@

\author{B. A. Weaver}
\affiliation{National Optical Astronomy Observatory, 950 N. Cherry Ave., Tucson, AZ 85719, USA}
